Verifying Demonstrations

### 2020-05-08 paper/DB-Schnorr-PKI.tex

@@

To establish \(k\), we use the \ac{DHKE}.
The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
\gDH^{\yDH}\) and both compute
\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
prime order \(\qDH\).
The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.

@@

The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
\(\UWBPR\), instead of a static \(k\).
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) (with a distance bound) whereas \(\DBSHW\) must perform \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ].
\] This means that the prover (and verifier) must prepare for the other proofs 
too.

The prover chooses \[
  \rho\rgets \ZZ_q, \quad
  \rhoDH\rgets \ZZ_{\qDH}, \quad
  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
  \rhoCL_{r'}\rgets \ZZ_{\qCL}
\] computes \[
  R\gets g^\rho, \quad
  \RDH\gets \gDH^{\rhoDH}, \quad
  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
\] and sends \(R, \RDH, \RCL\) to the verifier.

The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
The prover computes responses
\begin{multline*}
  s_i\gets \rho - c_i\alpha, \quad
  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
\end{multline*}
for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).

@@

>>>>

    \midrule
    \multicolumn{3}{c}{\textbf{Signature reblinding}} \\

@@

To establish \(k\), we use the \ac{DHKE}.
The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
\gDH^{\yDH}\) and both compute
\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
prime order \(\qDH\).
The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.
They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
\(\UWBPR\), instead of a static \(k\).

\paragraph*{Signature reblinding}

The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) (with a distance bound) whereas \(\DBSHW\) must perform \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ].
\] This means that the prover (and verifier) must prepare for the other proofs 
too.

This blinding procedure can be done once, there is no point in presenting the 
verifier with several different blindings of the same signature.

@@

Now we prepare for the actual \acl{DB}.
The prover chooses \[
  \rho\rgets \ZZ_q, \quad
  \rhoDH\rgets \ZZ_{\qDH}, \quad
  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
  \rhoCL_{r'}\rgets \ZZ_{\qCL}
\] computes \[
  R\gets g^\rho, \quad
  \RDH\gets \gDH^{\rhoDH}, \quad
  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
\] and sends \(R, \RDH, \RCL\) to the verifier.

The verifier chooses \(m\) challenges of length \(l\), \[
  c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l,
\] and sends these to the prover.
The prover computes responses
\begin{multline*}
  s_i\gets \rho - c_i\alpha, \quad
  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
\end{multline*}
for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).

@@

The setup, distance bounding and verification phases are repeated \(n\) times.
